Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-17 paper/lncsFormat.tex
finish sec 2.1.2; 5422 words (related works)(event detection).(with extra information).

The second group methods detect events by \textit{leveraging extra information}. 
\cite{huang2016efficient} incorporates user's and the followees' profiles in microblog platform as the extra information for modeling user's long term interests, and further detects the bursty events which draws the attention of users with different interests. 
However many event detection scenes only provide the microblog stream without user profile information and the following network. 
FrameNet?.
Wikipop\cite{ciglan2010wikipop}.
\cite{mcminn2013building} leverages LSH, wikipedia to build a large corpus for evaluating event detection on twitter.
\cite{osborne2012bieber} utilizes Wikipedia for filtering spurious events.
\cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
%The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.

>>>>

The second group methods detect events by \textit{leveraging extra information}. 
\cite{huang2016efficient} incorporates user's and the followees' profiles in microblog platform as the extra information for modeling user's long term interests, and further detects the bursty events which draws the attention of users with different interests. 
However many event detection scenes only provide the microblog stream without user profile information and the following network.
\cite{osborne2012bieber} compares two time series generated by event-related tweets and corresponding Wikipedia article's page views, and further filter out spurious events of microblogs.
Twevent \cite{Twevent2012} divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia, then detect the bursty segments and cluster these segments into candidate events for necessary post processings.
But Twevent is still hampered by the performance of simply clustering the bursty segments shown by \cite{Yan:2015wm}.
If not limited to microblog stream, many systems also use the extra information for improving event detection.
\cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
And \cite{liuleveraging2016} leverages the ACE corpus\cite{doddington2004automatic} and the structure of FrameNet\cite{baker1998berkeley} to improve the event detection within FrameNet, but has not shown how to apply the knowledge base for more general unstructured corpus.
In a nutshell, existing works are different from ours, as we transfer the category information of knowledge base into microblog's words and get the finer processing objects in event detection, rather than treating the knowledge base as a lookup table or a comparison base.
%Wikipop\cite{ciglan2010wikipop} uses the statistics of page views on Wikipedia articles to detect the personalized events.
%\cite{mcminn2013building} leverages LSH, wikipedia to build a large corpus for evaluating event detection on twitter.
%The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
